Pottery decor as networks on the Middle Niger

### 2023-08-03 analysis/paper/paper.Rmd
code style

# Graph of mean edge weight of the different communities
g1 <- mean_edge_weight |>
  pivot_longer(!community, names_to = "key",
               values_to = "mean_edge_weight") |>
  ggplot(aes(x = community, y = mean_edge_weight)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_grey() +
  theme_publish() +
  ylab("mean edge weight")

# Graph of centralization of the different communities
g2 <- tibble(centralization) |>
  mutate(community = 1:3) |>
  pivot_longer(!community, names_to = "key", values_to = "centralisation") |>
  ggplot(aes(x = community, y = centralisation)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_grey() +
  theme_publish()

>>>>

# Graph of mean edge weight of the different communities
g1 <- mean_edge_weight |>
  pivot_longer(!community, names_to = "key",
               values_to = "mean_edge_weight") |>
  ggplot(aes(x = community, y = mean_edge_weight)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_grey() +
  theme_bw() +
  ylab("mean edge weight")

# Graph of centralization of the different communities
g2 <- tibble(centralization) |>
  mutate(community = 1:3) |>
  pivot_longer(!community, names_to = "key", values_to = "centralisation") |>
  ggplot(aes(x = community, y = centralisation)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_grey() +
  theme_bw()
